quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-10-24 paper-quollr.Rmd
Updated Figure 8 caption

```{r linkerror, echo=TRUE, eval=knitr::is_html_output(), fig.cap="Interactive link plots showing the link between the NLDR layout (left) and the fitted model overlaid with the data in $7\\text{-}D$ (right) using `langevitour`. Brushing in either view highlights the corresponding subset of points across both representations, allowing examination of how well the NLDR layout preserves the underlying `Scurve` structure. Double-clicking on either view clears the selection and dehighlights all points.", layout = "l-page"}

@@

```{r, echo=TRUE, eval=knitr::is_html_output(), fig.cap="Link plots showing the relationship between the distribution of residuals (left), NLDR layout (middle) and the fitted model overlaid with the data in $7\\text{-}D$ (right) using `langevitour`.", layout = "l-page"}

@@

```{r, echo=TRUE, eval=knitr::is_html_output(), fig.cap="Interactive link plots showing the link between the NLDR layout (left) and the fitted model overlaid with the data in $7\\text{-}D$ (right) using `detourr`. Brushing in either view highlights the corresponding subset of points across both representations, allowing examination of how well the NLDR layout preserves the underlying `Scurve` structure. To highlight points in `detourr`, use the Select button. Double-clicking on either view clears the selection and dehighlights all points.", layout = "l-page"}

@@

```{r, echo=TRUE, eval=knitr::is_html_output(), fig.cap="Link plots showing the relationship between the distribution of residuals (left), NLDR layout (middle) and the fitted model overlaid with the data in $7\\text{-}D$ (right) using `detourr`.", layout = "l-page"}

>>>>

```{r linkerror, echo=TRUE, eval=knitr::is_html_output(), fig.cap="Interactive link plots showing the link between the UMAP layout (left) and the fitted model overlaid with the data in $7\\text{-}D$ (right) using `langevitour`. Brushing in either view highlights the corresponding subset of points across both representations, allowing examination of how well the UMAP layout preserves the underlying `Scurve` structure. Double-clicking on either view clears the selection and dehighlights all points.", layout = "l-page"}

@@

```{r, echo=TRUE, eval=knitr::is_html_output(), fig.cap="Interactive link plots showing the link between the residual distribution (left), the UMAP layout (middle) and the fitted model overlaid with the data in $7\\text{-}D$ (right) using `langevitour`. Brushing in any view highlights the corresponding subset across all panels, allowing detailed inspection of how residuals relate to both the UMAP embedding and the $p\\text{-}D$ structure. Points with higher residuals typically correspond to sparse or bridging regions in the UMAP layout and the less dense ends of the Scurve, whereas low-residual points tend to cluster within denser, well-preserved regions. Double-clicking clears the selection and resets all highlights.", layout = "l-page"}

@@

```{r, echo=TRUE, eval=knitr::is_html_output(), fig.cap="Interactive link plots showing the link between the UMAP layout (left) and the fitted model overlaid with the data in $7\\text{-}D$ (right) using `detourr`. Brushing in either view highlights the corresponding subset of points across both representations, allowing examination of how well the UMAP layout preserves the underlying `Scurve` structure. To highlight points in `detourr`, use the Select button. Double-clicking on either view clears the selection and dehighlights all points.", layout = "l-page"}

@@

```{r, echo=TRUE, eval=knitr::is_html_output(), fig.cap="Interactive link plots showing the link between the residual distribution (left), the UMAP layout (middle) and the fitted model overlaid with the data in $7\\text{-}D$ (right) using `detourr`. Brushing in any view highlights the corresponding subset across all panels, allowing detailed inspection of how residuals relate to both the UMAP embedding and the $p\\text{-}D$ structure. Points with higher residuals typically correspond to sparse or bridging regions in the UMAP layout and the less dense ends of the Scurve, whereas low-residual points tend to cluster within denser, well-preserved regions. To highlight points in `detourr`, use the Select button. Double-clicking clears the selection and resets all highlights.", layout = "l-page"}
